Light Transport Techniques for Tensor Field Visualization

### 2019-08-11 beamer2thesis/dummy.tex
update

\frame{
\frametitle{{Light Transport Gradient (LTG) - Isotropic field}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{itemize}
	\item Isotropic test field reveals offset response for the approach
	\bigskip
	\item natural shift against the inital light source (slice) direction (left)\\
%	$\Rightarrow$ initial light source configurations located close and pointing towards borders, are biased for low LTG (FTLE) responses
\end{itemize}
\end{small}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\caption*{\textit{Isotropic test field}}\bigskip
\begin{minipage}{.49\textwidth}
\includegraphics[height=\textwidth]{isotropic2.png} \caption*{a)~Glyphs}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[height=\textwidth]{iso_ftle.png} \caption*{b)~LTG($0^\circ$)}
\end{minipage}

@@

\end{column}
\end{columns}

} % END OF FRAME

>>>>

\frame{
\frametitle{{Fundamentals - Finite-Time Lyapunov Exponents (FTLE)}}

\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Definition}}
Local: 
$
	\mathop{FTLE} = \frac{1}{\lvert T\rvert}\ln \frac{\Delta}{\delta}
$ (cf. Fig. b))\\
Global: 
$
	\mathop{FTLE}(\mathbf{x})=\frac{1}{\lvert T\rvert}\ln \|\nabla\mathbf{u(x)}\|_2
$\\
{\tiny where $\| A\| _2 = \sqrt{\lambda_{\max}(A^TA)}$ is the spectral norm of matrix $A$}
\end{block}
\end{small}
\begin{itemize}
	\item measure for separation abilities of time-variant systems
	\item Lagrangian view in vector fields: placing particle, moving with flow
\end{itemize}

\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\centering
\begin{minipage}{0.85\textwidth}
\centering
\includegraphics[height=0.6\textwidth]{diverge_rot.png} {\scriptsize a)}
\includegraphics[height=0.6\textwidth]{ftle_sep.pdf} {\scriptsize b)}
\caption*{a) Vector field, b) Diverging pathlines}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\source{b) Skript Prof. Sadlo, SciVis SS2017}
\end{minipage}

@@

\end{column}
\end{columns}
} % END OF FRAME
